### 2014-05-07 intro.tex
Revise intro

\textbf{Sprout} (Chapter~\ref{chap:sprout}) is a transport protocol
designed to carry high-throughput interactive traffic, such as a
videoconference, over a cellular network. Sprout includes an explicit
model of the dynamics of cellular networks and makes predictions about
future network performance by inferring, with uncertainty, the current
state of the network and then extrapolating forward. Its control
strategy---how much data to send at a given moment---is a function
of those predictions and of an explicit objective: maximize
throughput, but bound in-network delays to be at most 100~ms with high probability.

\textbf{Remy} (Chapter~\ref{chap:remy}) expands Sprout to the
classical problem of \emph{multi-agent} congestion control, where many
applications may contend for the same limited network resource. Remy
is a protocol-design tool that takes, as input, a set of
assumptions about the uncertain network and workload, and an objective
to pursue on behalf of the application. Remy generates
congestion-control protocols, which we compare with conventional
protocols in simulation.

Once we had a computerized protocol designer, we explored using it as
a tool to gain understanding about the problem of congestion control.
How easy is it to ``learn'' a network protocol to achieve desired
goals, given a necessarily imperfect model of the networks where it
ultimately will be deployed? Is there a tradeoff between the
performance of an algorithm now---if optimized for a very specific
network---versus the protocol's ability to perform adequately as the
network evolves? Our experimentation into these questions of
``learnability'' is reported in Chapter~\ref{chap:learnability}.

>>>>

\textbf{Sprout} (Chapter~\ref{chap:sprout}) is a transport protocol
designed to carry high-throughput interactive traffic, such as a
videoconference, over a cellular network. Sprout includes an explicit
model of the dynamics of cellular networks and makes predictions about
future network performance by inferring, with uncertainty, the current
state of the network and evolving the model forward. Its control
strategy---how much data to send at a given moment---is a function of
those predictions and of an explicit objective: maximize throughput,
but bound in-network delays to be at most 100~ms with high
probability. On commercial cellular networks, Sprout gives 2-to-4
times the throughput and 7-to-9 times less delay than Skype, Apple
Facetime, and Google Hangouts.

\textbf{Remy} (Chapter~\ref{chap:remy}) expands Sprout to the
classical problem of \emph{multi-agent} congestion control, where many
applications may contend for the same limited network resource. Remy
is a protocol-design tool that takes, as input, a set of assumptions
about the uncertain network and workload, and an objective to pursue
on behalf of the application. Remy's computer-generated algorithms can
achieve higher performance and greater fairness than some
sophisticated human-designed schemes, including ones that put
intelligence inside the network.

Once we had a computerized protocol designer, we explored using it as
a tool to gain understanding about the problem of congestion control.
How easy is it to ``learn'' a network protocol to achieve desired
goals, given a necessarily imperfect model of the networks where it
ultimately will be deployed? Is there a tradeoff between the
performance of an algorithm now---if optimized for a very specific
network---versus the protocol's ability to perform adequately as the
network evolves? What is the cost of compatibility with existing TCP
congestion-control mechanisms? Our experimentation into these
questions of ``learnability'' is reported in
Chapter~\ref{chap:learnability}.
